Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2018-12-28 Tex/LaTeX2e Style File/Trindade_IEEE_TC_r0.tex
updating text

\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions. %, usually provided by manufacturers; the PV generator model is now completely determined.
%; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
%
%If the PV cells are in parallel, then there is a parallel array. Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
%
%\begin{equation}
%\label{eq:Iarray}
%I_{array} = (N_{cells in parallel})(I_{one cell})
%\end{equation}
%
%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
%
%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
%
%\begin{equation}
%\label{eq:Varray}
%V_{array} = (N_{cells in series})(V_{one panel})
%\end{equation}
%
%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
%------------------------------------------------------------
\subsection{The Battery Storage Model }
\label{sec:BATmodel}
%------------------------------------------------------------

@@

%\subsection{Cyber-physical systems x Energy x ESBMC}
%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes. Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa. The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology. The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments. CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole. 
%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}. For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies. Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation). 
%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled. Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations. 
%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification. Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver. This work tracks the same path. 
%----------------------------------------
\section{Model Checking Stand-alone Solar Photovoltaic Systems }
\label{sec:Methodology}
%----------------------------------------
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%\includegraphics[width=0.5\textwidth]{statetransition}
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to critical month method~\cite{Pinho}.
\includegraphics[width=0.4\textwidth]{flowchart_verification5.png}
\caption{Flowchart of the proposed automated verification of PV systems.}
\label{fig:flowchartgeneral}
In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed. 
%As a consequence, all the formulae of the employed mathematical models will also be updated. 
In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

@@

%------------------------------------------
\subsection{Objectives and Setup}
%------------------------------------------
Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
\end{enumerate}
All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3}. 
% enabled with the goal of reducing memory usage; 
We have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}. %The experiments were performed without a predefined timeout.

@@

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
%The description of our experimental results can be broken down into two parts: 
(a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel. This verification took approximately 63.3 hours to be performed. Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level. Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries. Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4. These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a month is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}, further affirming RQ1; after the sun rises, the systems returns to normal condition operation.

The same five case studies were evaluated by HOMER Pro. The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
%
Despite the divergence of results for the houses 1, 2, 3 and 4 w.r.t. our proposed approach, it is evident that the information collected from the dwellers indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2. House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
%
%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components. Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions. The season has impact since the case studies are from the rain forest, where clouds are always present. As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

@@

To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to test real PV systems.

>>>>

\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions. %, usually provided by manufacturers; t

The PV generator model is now completely determined. It requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
%
%If the PV cells are in parallel, then there is a parallel array. Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
%
%\begin{equation}
%\label{eq:Iarray}
%I_{array} = (N_{cells in parallel})(I_{one cell})
%\end{equation}
%
%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
%
%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
%
%\begin{equation}
%\label{eq:Varray}
%V_{array} = (N_{cells in series})(V_{one panel})
%\end{equation}
%
%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
%------------------------------------------------------------
\subsection{The Battery Storage Model }
\label{sec:BATmodel}
%------------------------------------------------------------

@@

%\subsection{Cyber-physical systems x Energy x ESBMC}
%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes. Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa. The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology. The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments. CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole. 
%
%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}. For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies. Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation). 
%
%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled. Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations. 
%
%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification. Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver. This work tracks the same path. 
%
%----------------------------------------
\section{Model Checking Stand-alone Solar Photovoltaic Systems }
\label{sec:Methodology}
%----------------------------------------
%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{flowchart_verification5.png}
\centering
\caption{Flowchart of the proposed automated verification of PV systems.}
\label{fig:flowchartgeneral}
\end{figure}

In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to critical month method~\cite{Pinho}. The equations to check the PV sizing were not presented at this paper, however the standard from Engineering Manual was the reference~\cite{Pinho}.
%
In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed. 
%As a consequence, all the formulae of the employed mathematical models will also be updated. 
In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

@@

%------------------------------------------
\subsection{Objectives and Setup}
%------------------------------------------
Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
\end{enumerate}

All experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning our verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 \phantom{}-boolector}. 
% enabled with the goal of reducing memory usage; 
We have also used the SMT solver Boolector version 2.4.1~\cite{Brummayer}. %The experiments were performed without a predefined timeout.

@@

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel. This verification took approximately 0.57 hours to be performed. In order to validate this possible flaw, it was surveyed the owner of the 1,200 W system; we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level. Our verification engine identified those flaws (for those three houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries. Our verification engine took approximately 5.1 hours to find this flaw in house 2; 5.8 hours for house 3, and 4.4 hours for house 4. These flaws were confirmed with the dwellers who own the systems by an interview process and from a local monitoring system with the Raspberry Pi controller: at least once a month is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}, further affirming RQ1; after the sun rises, the systems returns to normal condition operation. One more time the flaws were not caused by misuse of the system by the dwellers. Fig. \ref{fig:loadcurve} shows the monitoring result for the load curve of house 2 from June to July of 2018 (5 weeks), without undesired peaks from power demand of even unexpected energy consumption. The house 1 had an inconclusive result with the automated verification, because the solver did not presented any result from the SMT verification.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{loadcurve.png}
\centering
\caption{Five weeks monitored load curve from House 1.}
\label{fig:loadcurve}
\end{figure}

The same five case studies were evaluated by HOMER Pro. The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed by HOMER Pro. Fig. \ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{homer.png}
\centering
\caption{Homer simulation screen.}
\label{fig:homerscreen}
\end{figure}
%
Despite the divergence of results for the houses 2, 3 and 4 w.r.t. our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2. House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
%
%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components. Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions. The season has impact since the case studies are from the rain forest, where clouds are always present. As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

@@

To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to use real PV systems.
